---
title: "data_science"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{data_science}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


Building up the data science skills net using the package


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(skillsNet)
```

## building skills clusters
```{r bulding R language skill cluster}

makeRootSkillCluster("Rlang"
                     , 1
                     , "2018-08-10"
                     ) %>% 
  rbind(makeSpecificSkillCluster("Dplyr"
                                 , "Rlang"
                                 , 0.5
                                 , "Usage of the Dyplr Package to perform the full range of data manipulation"
                                 , "2018-01-01"
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Data.table"
                                 , "Rlang"
                                 , 1
                                 )) ->
    test_data
```

```{r showing structure}
head(test_data)
```

```{r Building communicating and influencing}
test_data %>% 
  rbind(makeRootSkillCluster("Comms_and_influence"
                             , 1
                             , "2017-10-10"
                             )) %>% 
  rbind(makeSpecificSkillCluster("Explaining complex concepts in basic ways"
                                 , "Comms_and_influence"
                                 , 1
                                 , "Communicating the complex work done in data science, such as analytical pipelines, data concerns and modelling decisions"
                                 , "2019-08-09" 
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Constructing and Hosting Knowledge shares"
                                 , "Comms_and_influence"
                                 , 1
                                 )) -> 
    test_data
```

```{r}
tail(test_data)
```


## Adding verification layer

Often, you want for a skills matrix to be supported or verified by a supervisor or management entity. To avoid issues of fraudulent or ignorant self-certification. 

By adding a verified by level, around which a series of authentications steps could be later built, then we have the basis of a fully flexible skills reporting database. 


```{r Adding Rlang verification}
test_data %>% 
  rbind(verifySpecificSkillCluster("Rlang", "Ace Bepson")) ->
    test_data
```


```{r showing off changes}
tail(test_data)
```

