---
title: "data_science"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{data_science}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


Building up the data science skills net using the package


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(skillsNet)
```

## building skills clusters

Within R there are many packages which are used to perform tasks. For the most part these are minor entities which only merit a small increase in depth. At times though there are substantial packages which generate a serious boost in productivity or which open up a wide range of entities.

As such the weighting system used is 

```{r defining weighting system}
minor_package <- 0.1 # casual stuff like ggrepel
major_package <- 0.5 # important but specialist stuff like dplyr and ggplot
extraordinary_package <- 1 # major and broad toolkits like mlr and data.table
```

```{r making wrapper for new packages}
newPackageCluster <- function(package_name, date = Sys.Date(), weight = minor_package){
    makeSpecificSkillCluster(skill_spec = package_name
                                 , skill_base_name = "Rlang"
                                 , skill_weight = weight
                                 , skill_comp_date = date
                                 ) %>% 
    return()
}
```

```{r bulding R language skill cluster}

makeRootSkillCluster("Rlang"
                     , 1.2
                     , "2018-08-10"
                     ) %>% 
  rbind(makeSpecificSkillCluster("Passive Familiarity"
                                 , "Rlang"
                                 , 0.25
                                 , "Familiar with the underlying concepts and mechanical descriptions are not foreign"
                                 , "2018-08-15"
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Active Familiarity"
                                 , "Rlang"
                                 , 0.75
                                 , "Familiar with mechanics needed to achieve practical concepts and a source of further learning is known"
                                 , "2018-09-30"
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Dplyr"
                                 , "Rlang"
                                 , major_package
                                 , "Usage of the Dyplr Package to perform the full range of data manipulation"
                                 , "2018-10-01"
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Package Creation"
                                 , "Rlang"
                                 , major_package
                                 , "Knowledge of how to build and release packages for use in R"
                                 , "2019-04-01"
                                 )) %>% 
  rbind(newPackageCluster("ggrepel", date = "2019-04-01")) %>% 
  rbind(newPackageCluster("ggplot", date = "2019-08-01", weight = major_package)) %>% 
  rbind(newPackageCluster("testthat")) %>% 
  rbind(newPackageCluster("devtools")) %>% 
  rbind(newPackageCluster("usethis", date = "2019-06-10")) %>% 
  rbind(newPackageCluster("config", date = "2019-01-02")) %>% 
  rbind(newPackageCluster("forcats")) %>% 
  rbind(newPackageCluster("lubridate", date = "2018-11-11")) %>% 
  rbind(newPackageCluster("tidyr")) %>% 
  rbind(makeSpecificSkillCluster("Data.table"
                                 , "Rlang"
                                 , extraordinary_package
                                 )) ->
    test_data
```




```{r }
head(test_data)
```

```{r Building communicating and influencing}
test_data %>% 
  rbind(makeRootSkillCluster("Comms_and_influence"
                             , 1.1
                             , "2017-10-10"
                             )) %>% 
    rbind(makeSpecificSkillCluster("Passive Familiarity"
                                 , "Comms_and_influence"
                                 , 0.25
                                 , "Familiar with the underlying concepts and mechanical descriptions are not foreign"
                                 , "2017-10-10"
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Active Familiarity"
                                 , "Comms_and_influence"
                                 , 0.75
                                 , "Familiar with mechanics needed to achieve practical concepts and a source of further learning is known"
                                 , "2017-10-10"
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Explaining complex concepts in basic ways"
                                 , "Comms_and_influence"
                                 , extraordinary_package
                                 , "Communicating the complex work done in data science, such as analytical pipelines, data concerns and modelling decisions"
                                 , "2019-08-09" 
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Constructing and Hosting Knowledge shares"
                                 , "Comms_and_influence"
                                 , minor_package
                                 )) -> 
    test_data
```

```{r}
tail(test_data)
```
```{r Financial Modelling}
test_data %>% 
  rbind(makeRootSkillCluster("Fin_models"
                             , 1.1
                             , "2017-08-10"
                             )) %>% 
    rbind(makeSpecificSkillCluster("Passive Familiarity"
                                 , "Fin_models"
                                 , 0.25
                                 , "Familiar with the underlying concepts and mechanical descriptions are not foreign"
                                 , "2017-08-10"
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Active Familiarity"
                                 , "Fin_models"
                                 , 0.75
                                 , "Familiar with mechanics needed to achieve practical concepts and a source of further learning is known"
                                 , "2019-08-26"
                                 )) -> test_data

tail(test_data)
```


## Adding verification layer

Often, you want for a skills matrix to be supported or verified by a supervisor or management entity. To avoid issues of fraudulent or ignorant self-certification. 

By adding a verified by level, around which a series of authentications steps could be later built, then we have the basis of a fully flexible skills reporting database. 


```{r Adding Rlang verification}
test_data %>% 
  rbind(verifySpecificSkillCluster("Explaining complex concepts in basic ways", "Ace Bepson")) ->
    test_data
```


```{r showing off changes}
tail(test_data)
```

