---
title: "data_science"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{data_science}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Appendix 1: Data Science skillsNet

Building up the data science skills net using the package


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup data_science testing elements}
library(skillsNet)
```

```{r defining add passive and active wrappers}
makePassiveCluster <- function(base_name, base_date = Sys.Date(), base_weight = 0.25){
  makeSpecificSkillCluster("Passive Familiarity"
                           , skill_base_name = base_name
                           , skill_weight = base_weight
                           , skill_desc = "Familiar with the underlying concepts and mechanical descriptions are not foreign"
                           , skill_comp_date = base_date
                          ) %>% 
    return()
}
makeActiveCluster <- function(base_name, base_date = Sys.Date(), base_weight = 0.75){
  makeSpecificSkillCluster("Active Familiarity"
                           , skill_base_name = base_name
                           , skill_weight = base_weight
                           , skill_desc = "Familiar with mechanics needed to achieve practical concepts and a source of further learning is known"
                           , skill_comp_date = base_date
                          ) %>% 
    return()
}

newRootSkill <- function(base_name, base_date = Sys.Date(), base_weight = 1.1){
  makeRootSkillCluster(base_name
                             , base_weight
                             , base_date
                             ) %>% 
    rbind(makePassiveCluster(base_name, base_date)) %>% 
    rbind(makeActiveCluster(base_name, base_date)) %>% 
    return()
}
```

## building skills clusters

Within R there are many packages which are used to perform tasks. For the most part these are minor entities which only merit a small increase in depth. At times though there are substantial packages which generate a serious boost in productivity or which open up a wide range of entities.

As such the weighting system used is 

```{r defining weighting system}
minor_package <- 0.1 # casual stuff like ggrepel
major_package <- 0.5 # important but specialist stuff like dplyr and ggplot
extraordinary_package <- 1 # major and broad toolkits like mlr and data.table
```

```{r making wrapper for new packages}
newPackageCluster <- function(package_name, date = Sys.Date(), weight = minor_package){
    makeSpecificSkillCluster(skill_spec = package_name
                                 , skill_base_name = "Rlang"
                                 , skill_weight = weight
                                 , skill_comp_date = date
                                 ) %>% 
    return()
}
```

```{r bulding R language skill cluster}

makeRootSkillCluster("Rlang"
                     , 1.2
                     , "2018-08-10"
                     ) %>% 
  rbind(makeSpecificSkillCluster("Passive Familiarity"
                                 , "Rlang"
                                 , 0.25
                                 , "Familiar with the underlying concepts and mechanical descriptions are not foreign"
                                 , "2018-08-15"
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Active Familiarity"
                                 , "Rlang"
                                 , 0.75
                                 , "Familiar with mechanics needed to achieve practical concepts and a source of further learning is known"
                                 , "2018-09-30"
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Dplyr"
                                 , "Rlang"
                                 , major_package
                                 , "Usage of the Dyplr Package to perform the full range of data manipulation"
                                 , "2018-10-01"
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Package Creation"
                                 , "Rlang"
                                 , major_package
                                 , "Knowledge of how to build and release packages for use in R"
                                 , "2019-04-01"
                                 )) %>% 
  rbind(newPackageCluster("ggrepel", date = "2019-04-01")) %>% 
  rbind(newPackageCluster("ggplot", date = "2019-08-01", weight = major_package)) %>% 
  rbind(newPackageCluster("testthat", date = "2019-06-11")) %>% 
  rbind(newPackageCluster("devtools", date = "2019-07-10")) %>% 
  rbind(newPackageCluster("usethis", date = "2019-06-10")) %>% 
  rbind(newPackageCluster("config", date = "2019-01-02")) %>% 
  rbind(newPackageCluster("forcats", date = "2019-01-01")) %>% 
  rbind(newPackageCluster("lubridate", date = "2018-11-11")) %>% 
  rbind(newPackageCluster("tidyr", date = "2019-05-05")) %>% 
  rbind(newPackageCluster("glue", date = "2019-09-11")) %>% 
  rbind(makeSpecificSkillCluster("Data.table"
                                 , "Rlang"
                                 , extraordinary_package
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Drake"
                                 , "Rlang"
                                 , major_package
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Shiny"
                                 , "Rlang"
                                 , extraordinary_package
                                 )) ->
    test_data
```




```{r }
head(test_data)
```



```{r Building communicating and influencing}
test_data %>% 
  rbind(makeRootSkillCluster("Comms_and_influence"
                             , 1.1
                             , "2017-10-10"
                             )) %>% 
    rbind(makeSpecificSkillCluster("Passive Familiarity"
                                 , "Comms_and_influence"
                                 , 0.25
                                 , "Familiar with the underlying concepts and mechanical descriptions are not foreign"
                                 , "2017-10-10"
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Active Familiarity"
                                 , "Comms_and_influence"
                                 , 0.75
                                 , "Familiar with mechanics needed to achieve practical concepts and a source of further learning is known"
                                 , "2017-10-10"
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Explaining complex concepts in basic ways"
                                 , "Comms_and_influence"
                                 , extraordinary_package
                                 , "Communicating the complex work done in data science, such as analytical pipelines, data concerns and modelling decisions"
                                 , "2019-08-09" 
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Constructing and Hosting Knowledge shares"
                                 , "Comms_and_influence"
                                 , minor_package
                                 , "Designing and running knowledge share sessions on Topics which there is a skill disparity"
                                 , "2019-09-15"
                                 )) -> 
    test_data
```

```{r}
tail(test_data)
```
```{r Financial Modelling}
test_data %>% 
  rbind(makeRootSkillCluster("Fin_models"
                             , 1.1
                             , "2017-08-10"
                             )) %>% 
    rbind(makeSpecificSkillCluster("Passive Familiarity"
                                 , "Fin_models"
                                 , 0.25
                                 , "Familiar with the underlying concepts and mechanical descriptions are not foreign"
                                 , "2017-08-10"
                                 )) %>% 
  rbind(makeSpecificSkillCluster("Active Familiarity"
                                 , "Fin_models"
                                 , 0.75
                                 , "Familiar with mechanics needed to achieve practical concepts and a source of further learning is known"
                                 , "2019-08-26"
                                 )) -> test_data

tail(test_data)
```

```{r Adding misc skills}
test_data %>% 
  rbind(newRootSkill("Acquiring_data", base_date = "2019-08-15")) %>% 
  rbind(newRootSkill("Understanding_customer_needs", base_date = "2019-08-15")) %>% 
  rbind(newRootSkill("Working_with_credibility", base_date = "2019-08-15")) %>% 
  rbind(newRootSkill("Presenting_and_disseminating_data_effectively", base_date = "2019-08-15")) %>% 
  rbind(newRootSkill("Leadership", base_date = "2019-08-15")) -> 
    test_data

```


```{r adding training framework}
test_data %>% 
  rbind(newRootSkill("GIS_Mapping", base_date = "2019-08-29")) %>% 
  rbind(makeSpecificSkillCluster("Leaflet", "GIS_Mapping", 0.25, "Understanding the leaflet package, and the elements in it")) %>% 
  
  rbind(makeSpecificSkillCluster("Altair", "Interactive_Viz", 0.1, "Understanding the Altair package, and the elements in it")) %>% 
  rbind(makeSpecificSkillCluster("ggplotly", "Interactive_Viz", 0.1, "Understanding the ggplotly package, and the elements in it")) %>% 
  rbind(makeSpecificSkillCluster("Highcharts", "Interactive_Viz", 0.1, "Understanding the Highcharts package, and the elements in it")) %>% 
  rbind(makeSpecificSkillCluster("d3.js", "Interactive_Viz", 0.5, "Understanding the d3.js package, and the elements in it")) %>% 
  rbind(newRootSkill("Interactive_Viz", base_date = "2019-08-29")) -> 
    test_data


```

```{r making tableau framework}
test_data %>% 
  rbind(newRootSkill("Tableau", base_date = "2019-05-01")) %>% 
  rbind(makeSpecificSkillCluster("Visual Analytics", "Tableau", 0.1, "Using Tableau to present data visually: Intro")) %>% 
  rbind(makeSpecificSkillCluster("Connecting to data", "Tableau", 0.25, "The various methods of connecting to data in tableau", "2019-07-01")) %>% 
  rbind(makeSpecificSkillCluster("Dashboards and Stories", "Tableau", 0.1, "Using the Dashboards and Stories elements within tableau to stich multiple visual analytics elements together")) %>% 
  rbind(makeSpecificSkillCluster("Mapping", "Tableau", 0.1, "Using tableau to plot geographical elements of an analysis")) %>% 
  rbind(makeSpecificSkillCluster("Calculations", "Tableau", 0.1, "Using the internal calculation language in tableau")) %>% 
  rbind(makeSpecificSkillCluster("R_integration", "Tableau", 0.1, "Using R functions within tableau to perform complex processes")) %>% 
  rbind(makeSpecificSkillCluster("Publishing", "Tableau", 0.1, "Using tableau online and tableau server to publish work to remote entities")) ->
  test_data

```

```{r Working with credibility}
test_data %>% 
  rbind(makeSpecificSkillCluster("QA Mechanisms: Explore level", "Working_with_credibility", 0.15, "Have explored and gained a level of familiarity with the ways that we can Assure Quality", "2019-10-02"))
```


## Adding verification layer

Often, you want for a skills matrix to be supported or verified by a supervisor or management entity. To avoid issues of fraudulent or ignorant self-certification. 

By adding a verified by level, around which a series of authentications steps could be later built, then we have the basis of a fully flexible skills reporting database. 


```{r Adding Rlang verification}
test_data %>% 
  rbind(verifySpecificSkillCluster("Explaining complex concepts in basic ways", "Ace Bepson")) ->
    test_data
```


```{r showing off changes}
tail(test_data)
```
```{r saving test data}
usethis::use_data(test_data, overwrite = TRUE)
```

